\vspace{5em}On Evaluating Adversarial Robustness

### 2019-02-19 paper.tex
Adding Alex as co-author

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen

>>>>

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2},
  Alexey Kurakin\textsuperscript{1}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen
